---
title: "CensusMap_Descriptive"
author: "H"
 
output:
  html_document:
    toc: true
    toc_float: true
---
 
Following codes create the map of socio-economic and demographic indicators from the data frame containing census vector of each year, which was created in the `censusVar_Mapping.Rmd` script.
 
Also saves census data locally `data/city/listCen.rds`
And Saves DA shape files to remote DB as well, to be intersected to intervention lines.
 
 
```{r setup, message=FALSE, warning=FALSE}
 
# Libraries
knitr::opts_chunk$set(echo = TRUE)
library(sf)
library(rgdal)
library(tidyverse)
library(cancensus)
library(ggmap)
library(stringr)
library(kableExtra)
library(htmlTable)
library(ggsankey)
library(grid)
library(gridExtra)
library(cowplot)
library(ggpubr)
library(RPostgres)
library(rpostgis)
library(readxl)
library(dplyr)

rm(list=ls())
 
# Canceuss 
#options(cancensus.cache_path = "cache/")
#set_cancensus_cache_path("cache/", install = TRUE)
options(cancensus.cache_path = "cache/.cancensus_cache")
 
bool_loadCensus = TRUE
 
# Plot global params 
theme_set(theme_classic())
theme_set(
  theme(
    axis.text.x = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks = element_blank(),
    rect = element_blank(), 
    text = element_text(size=12), 
    plot.title = element_text(size=15),   
    legend.text = element_text(size = 12),
    legend.title = element_text(size = 12)
    )
)
 
 
# Load census vector names for each year 
dfCensVec <- readRDS("censMappedVars.rds")
 
 
# Variable name description 
dfVarDesc<- data.frame(Description = c(
  "Visible Minority", 
  "Indigenous identity", 
  "Max High sch, 15",
  "Max High sch, 25-64",
  "No High sch, 15",
  "No High sch, 25-64",
  "Moved past 5 yrs", 
  "Moved past 1 yr", 
  "Low-income cutoff", 
  "Recent immigrants",
  "Age below 15", 
  "Age over 65", 
  ">30% of income for housing", 
  "Tenant, as opposed to owner"), 
  varName = c(
    "i_visMin",
    "i_aboriginal",
    "i_educ_15",
    "i_educ_25_64",
    "i_educ_noHS_15",
    "i_educ_noHS_25_64",
    "i_move_5yrs",
    "i_move_1yrs",
    "i_LICO",
    "i_rec_imm",
    "i_young",
    "i_old",
    "i_tenant_30income",
    "i_tenant"
  ), 
varShortName =c(
  "Visible minorities",
  "Aboriginal",
  "High school",
  "Education_25",
  "No High school",
  "No High school 25",
  "Recent movers",
  "Recent move_1yr",
  "Low income",
  "Recent immigrants",
  "Children",
  "Seniors",
  "Housing expense",
  "Tenants")
)
 
 
 
```
 
Download census data based on the identified vector names, and create proporiton measures for each dissemination area. Rehspaed for facet map originally, but protting through looping. 
```{r}
funcGetCensVector <- function(df, dfVarDesc){
  # Calculate proportions
  df <- funcCensusIndicator(df)
  # Make it long if used for facet plot  
  dfMapLong <- df %>% 
    select(starts_with("i_")) %>% 
    pivot_longer(cols = starts_with("i_"), names_to = "x",values_to = "y")
  # Join sf with variable description
  dfMapLong <- dfMapLong %>% 
    left_join(dfVarDesc, by = c("x"="varName"))
  return(dfMapLong)
}

funcGetBoroVector <- function(df, dfVarDesc, Population_W){
  # Calculate proportions
  df <- funcBoroIndicator(df, Population_W)
  # Make it long if used for facet plot  
  dfMapLong <- df %>% 
    select(starts_with("i_")) %>% 
    pivot_longer(cols = starts_with("i_"), names_to = "x",values_to = "y")
  # Join sf with variable description
  dfMapLong <- dfMapLong %>% 
    left_join(dfVarDesc, by = c("x"="varName"))
  return(dfMapLong)
}
 
 
 
# function to create variable name 
# funcCensusIndicator <- function(df,Population_W){
#   df %>% 
#     mutate(i_visMin = Population_W*(visibleMin_count/visibleMin_denom), #yes
#            i_aboriginal = indigi_count/indigi_denom, #no
#            i_educ_15 = educ_HS_count_15yr/educ_HS_denom_15yr, #no
#            i_educ_25_64 = educ_HS_count_25_64yr/educ_HS_denom_25_64yr, #no
#            i_educ_noHS_15 = educ_no_HS_count_15yr/educ_HS_denom_15yr,  #no
#            i_educ_noHS_25_64 = Population_W*(educ_no_HS_count_25_64yr/educ_HS_denom_25_64yr),  #yes
#            i_move_5yrs = Population_W*(move_5yr_count/move_5yr_denom), #yes
#            i_move_1yrs = move_1yr_count/move_1yr_denom, #no
#            i_LICO = Population_W*(LICO_prevalence*0.01), #make it to proportion  #yes
#            i_rec_imm = Population_W*(recentImmig_count/recentImmig_denom), #yes
#            i_young = Population_W*(age_1_14_count/age_denom), #yes
#            i_old =  Population_W*(age_64_over/age_denom), #yes
#            i_tenant_30income = housingExpend_30_count/property_denom, #no
#            i_tenant = Population_W*(tenant_count/(property_denom))#yes
#     ) %>% 
#     select(i_visMin, i_educ_noHS_25_64, i_move_5yrs, i_LICO, i_rec_imm, i_young, i_old, i_tenant)
# }

funcCensusIndicator <- function(df){
  df %>% 
    mutate(i_visMin = (visibleMin_count/visibleMin_denom), #yes
           i_aboriginal = indigi_count/indigi_denom, #no
           i_educ_15 = educ_HS_count_15yr/educ_HS_denom_15yr, #no
           i_educ_25_64 = educ_HS_count_25_64yr/educ_HS_denom_25_64yr, #no
           i_educ_noHS_15 = educ_no_HS_count_15yr/educ_HS_denom_15yr,  #no
           i_educ_noHS_25_64 = (educ_no_HS_count_25_64yr/educ_HS_denom_25_64yr),  #yes
           i_move_5yrs = (move_5yr_count/move_5yr_denom), #yes
           i_move_1yrs = move_1yr_count/move_1yr_denom, #no
           i_LICO = (LICO_prevalence*0.01), #make it to proportion  #yes
           i_rec_imm = (recentImmig_count/recentImmig_denom), #yes
           i_young = (age_1_14_count/age_denom), #yes
           i_old =  (age_64_over/age_denom), #yes
           i_tenant_30income = housingExpend_30_count/property_denom, #no
           i_tenant = (tenant_count/(property_denom))#yes
    ) %>% 
    select(i_visMin, i_educ_noHS_25_64, i_LICO, NOM)
}

funcBoroIndicator <- function(df,Population_W){ # df <- mtl_Boro # get covariates
  df <- df %>%
    mutate(i_visMin = Population_W*(visibleMin_count/visibleMin_denom), #yes
           i_educ_noHS_25_64 = Population_W*(educ_no_HS_count_25_64yr/educ_HS_denom_25_64yr),  #yes
           #i_move_5yrs = Population_W*(move_5yr_count/move_5yr_denom), #yes
           i_LICO = Population_W*(LICO_prevalence*0.01), #make it to proportion  #yes
           i_rec_imm = Population_W*(recentImmig_count/recentImmig_denom), #yes
           i_young = Population_W*(age_1_14_count/age_denom), #yes
           i_old =  Population_W*(age_64_over/age_denom), #yes
           i_tenant = Population_W*(tenant_count/(property_denom))#yes
     ) %>%
    replace(is.na(.), 0) %>% 
    select(NOM,i_visMin, i_educ_noHS_25_64, i_LICO)
  
  df %>%
    group_by(NOM) %>% 
    summarise(across(c(i_visMin,
                       i_educ_noHS_25_64,
                       #i_move_5yrs,
                       i_LICO), sum))
}
 
```
 
 
### 2021 data 
```{r}
options(cancensus.api_key = "CensusMapper_91294cf61b6144bca0fcac3333a180b6")
options(cancensus.cache_path = "./")

# Following codes will extract the census vectors, along with polygons 
b <- dfCensVec %>% pull(X2021)
b <- setNames(b, rownames(dfCensVec)) # Make it named vector so that variable names will be passed to extracted census vars  
 
 
mtl_2021 <- get_census(dataset="CA21", 
                 regions=list(CMA='24462'), 
                 vectors=b,
                 level= "CT", 
                 use_cache = TRUE, 
                 geo_format = "sf", 
                 quiet = TRUE, 
                 api_key = Sys.getenv("CM_API_KEY")) %>% #### NEED to use your own API KEY 
    mutate(interact_aoi = (CD_UID %in% c(2466, 2465, 2458)) & !(CSD_UID %in% c(2458033, 2458037))) %>% 
    mutate(hiroshi_old_aoi = (CSD_UID %in% c("2466127", "2466117", "2465005", "2466112","2466007", "2466023", "2466087", "2466097", "2466032", "2466107" , "2458227", "2458007") 
    ))


## Get boroughs and related cities of MTL
mtl<-st_read("limites-administratives-agglomeration.shp")

# mtl2<-get_census(dataset="CA21", 
#                  regions=list(CMA='24462'), 
#                  vectors=b,
#                  level= "CSD", 
#                  use_cache = TRUE, 
#                  geo_format = "sf", 
#                  quiet = TRUE, 
#                  api_key = Sys.getenv("CM_API_KEY")) 

mtl_2021 <- mtl_2021 %>% filter(interact_aoi == TRUE )


ggplot(mtl_2021) + geom_sf(aes(fill=Population)) + geom_sf(data=mtl, color = "white", fill = NA)
#ggplot(mtl2) + geom_sf(aes(fill=Population)) + geom_sf(data=mtl, color = "white", fill = NA)

### ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++ ###
# Get the Boro level count
### ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++ ###
# mtl_Boro <- mtl_2021  %>%
#   st_join(mtl, largest = TRUE) %>%
#   filter(!is.na(NOM)) %>% 
#   replace(is.na(.), 0) %>%
#   group_by(NOM) %>% 
#   summarise(across(c(Population,
                     # visibleMin_count,
                     # visibleMin_denom,
                     # educ_no_HS_count_25_64yr,
                     # educ_HS_denom_25_64yr,
                     # LICO_prevalence,
                     # recentImmig_count,
                     # recentImmig_denom,
                     # age_1_14_count,
                     # age_64_over,
                     # age_denom,
                     # tenant_count,
                     # property_denom), sum)) #%>% ggplot() + geom_sf()
# mtl_Boro <- mtl_Boro[-12,] #remove L'ﾃ四e-Dorval area

# get boro information for the mtl_2021(CT level)
mtl_Boro <- mtl_2021  %>%
  st_join(mtl, largest = TRUE) %>%
  filter(!is.na(NOM)) %>% 
  replace(is.na(.), 0)
mtl_Boro_Total <- mtl_Boro %>%
  group_by(NOM) %>% 
  summarise(Population = sum(Population))
ggplot(mtl_Boro_Total) + geom_sf(aes(fill=Population)) 

### ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++ ###
# r = total count in Monreal/all population in Montreal
# r= sum of count in all borogh/all population in all boroght
# E_i = pop_i * r
# i is borough
### ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++ ###
# Population_W <- mtl_Boro_Total$Population/sum(mtl_Boro_Total$Population) #for each boro_i=pop_i/sum_all_i(pop_i)
# mtl_Boro_Total$Expected_count_for_each_boro <- round(sum(last_week_2021_new_cases_total$last_week_2021_new_cases_total)*Population_W, 0)

### ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++ ###
Population_W <- mtl_Boro_Total$Population/sum(mtl_Boro_Total$Population) #for each boro_i=pop_i/sum_all_i(pop_i)
mtl_Boro_Total$Expected_count_for_each_boro <- round(sum(last_week_2021_new_cases_total$last_week_2021_new_cases_total)*Population_W, 0)

### ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++ ###
# Get the weight for each CT area in each Boro, add this col to mtl_Boro
### ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++ ###

mtl_Boro_weight <- mtl_Boro %>% 
  select(Population,GeoUID, NOM) %>% 
  st_drop_geometry() %>%
  left_join(mtl_Boro_Total, by = c("NOM" = "NOM")) %>%
  rename("Population_CT" = "Population.x") %>%
  rename("Population_Boro" = "Population.y") 

# Weighted by Population_CT/Population_Boro
mtl_Boro$Population_W <- mtl_Boro_weight$Population_CT/mtl_Boro_weight$Population_Boro
summary(mtl_Boro$Population_W)

ggplot(mtl_Boro) + 
  geom_sf(aes(fill=Population_W)) + 
  geom_sf(data=mtl, color = "white", fill = NA) + 
  ggtitle("2021 Weighted(By borough level) Population for each CT area")
# get_census(dataset="CA21", 
#                   regions=list(CMA='24462'), 
#                   vectors=b,
#                   level= "CSD",  #CD
#                   use_cache = TRUE, 
#                    geo_format = "sf", 
#                    quiet = TRUE, 
#                    api_key = Sys.getenv("CM_API_KEY")) 

#a <- mtl_Boro_1 %>% filter(NOM=="Verdun")
```
 
```{r}
plot_case <- my_data3 %>% 
  select(last_week_2021_new_cases_total,geometry.x)

# Create the map
ggplot(data = plot_case) +
  geom_sf(aes(fill = last_week_2021_new_cases_total, geometry = geometry.x)) +
  scale_fill_viridis_c() + # Optional: use a color scale for better visualization
  theme_map() +
  labs(title = "Distribution of one week cases in 2021 observed",
       fill = "Weekly cases in 2021 observed",
       caption = "Source: https://github.com/jeremymoreau/covid19mtl/tree/master/app/data/sources")

```


### Pop density  
```{r}
# library(magrittr)
# mtl_2021  %<>%  mutate(popDensity_per1000 = Population/`Shape Area`/1000)
#  
# ggplot() + 
#   geom_sf(data = mtl_2021, aes(fill= popDensity_per1000))
 
```
 
 
Corr plots 
```{r fig.width = 10}
mtl_Boro %>% 
  funcCensusIndicator  %>% 
  select(starts_with("i_")) %>% 
  st_drop_geometry() %>% 
  cor(use = "complete.obs") %>% 
  corrplot::corrplot.mixed(number.cex = 0.5, tl.cex = 0.5)

### ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++ ###
# Get Cor_plot of the Covariates for each Boro
### ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++ ###
# a <- mtl_Boro %>% 
#   group_by(NOM) %>% 
#   summarise(visibleMin_prop = sum((visibleMin_count/visibleMin_denom) * Population_W))
# class(a)
# 
# ggplot(a) + geom_sf(aes(fill = visibleMin_prop))

Predictor_var <- funcBoroIndicator(mtl_Boro, mtl_Boro$Population_W)
funcBoroIndicator(mtl_Boro, mtl_Boro$Population_W)  %>% 
  select(starts_with("i_")) %>% 
  st_drop_geometry() %>% 
  cor(use = "complete.obs") %>% 
  corrplot::corrplot.mixed(number.cex = 0.5, tl.cex = 0.5)

# x = Predictor_var[,2:8] %>% st_drop_geometry();
# x <- scale(x, center = TRUE, scale = TRUE)
# # Convert the scaled data back to a data frame
# x <- as.data.frame(x)
# 
# x %>% 
#   cor(use = "complete.obs") %>% 
#   corrplot::corrplot.mixed(number.cex = 0.5, tl.cex = 0.5)
```
 
 
### Plot proportion maps for 2021 -  Scales vary across maps !-------------------------------------------
```{r fig.width=8, fig.height=8}
## For CT
dfMapLong_mtl_2021 <- funcGetCensVector(mtl_Boro, dfVarDesc)
 
# Generate plot with descriptive name 
pList_mtl_2021 <- list()
 
for(i in dfVarDesc$Description){
  pList_mtl_2021[[i]] <-  dfMapLong_mtl_2021 %>%
    filter(Description == i) %>% 
    ggplot() +
    geom_sf(inherit.aes = FALSE, aes(fill = y), size =0.5, color= "black") + 
    ggtitle(i) + 
    theme(legend.position = "bottom") + 
    theme(legend.text=element_text(size=9))
}
 
 
# And plot 
pList_mtl_2021

### ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++ ###
## For Boro
dfMapLong_mtl_2021 <- funcGetBoroVector(mtl_Boro, dfVarDesc, mtl_Boro$Population_W)
 
# Generate plot with descriptive name 
pList_mtl_2021 <- list()
 
for(i in dfVarDesc$Description){
  pList_mtl_2021[[i]] <-  dfMapLong_mtl_2021 %>%
    filter(Description == i) %>% 
    ggplot() +
    geom_sf(inherit.aes = FALSE, aes(fill = y), size =0.5, color= "black") + 
    ggtitle(i) + 
    theme(legend.position = "bottom") + 
    theme(legend.text=element_text(size=9))
}
 
 
# And plot 
pList_mtl_2021

last_week_2021_new_cases_total %>% 
    ggplot() +
    geom_sf(inherit.aes = FALSE, aes(fill = y), size =0.5, color= "black") 
 
```

making traffic in each borough
```{r}
## Connect to Data
library(rpostgis)
library(RPostgreSQL)
library(RPostgres)

# Create an object that has connection to remote Database whose aDDress is 132.... anD name of Db is safegraph
conObesity <- RPostgreSQL::dbConnect("PostgreSQL", host = "132.216.183.3",
                                     dbname = "safegraph", user = "chizhang",
                                     password = "*******")

# Write query to get Data - Data are too big, so DownloaD the first 100,000 only. I will later show how to DownloaD quebec Data only.  
#q <- "select * from ca_od_long where province = 'QC';"
q <- "select * from ca_od_long where province = 'QC' and Y = 2021 and m=12;"
#q <- "select * from ca_od_long where province = 'QC' and Y = 2022 ;"
#q <- "select * from ca_oD_long limit 30000:400000;"

# SenD query to the Database
routing <- dbGetQuery(conObesity, q)
```

```{r}
library("devtools")
library(dplyr)
library(tmap)
library(sf)
library(cancensus)

options(cancensus.api_key = "CensusMapper_91294cf61b6144bca0fcac3333a180b6")
options(cancensus.cache_path = "./")

DA <- get_census(dataset='CA21', 
                 regions=list(CMA = "24462"),
                 level='DA', use_cache = FALSE, geo_format = "sf", quiet = TRUE, 
                 api_key = Sys.getenv("CM_API_KEY")) %>%
  st_transform(crs = 2959)


CT <- get_census(dataset='CA21', 
                 regions=list(CMA = "24462"),
                 level='CT', use_cache = FALSE, geo_format = "sf", quiet = TRUE, 
                 api_key = Sys.getenv("CM_API_KEY")) %>%
  st_transform(crs = 2959)

mtl <- st_transform(mtl, 2959)
DA_mtl <- DA %>% st_join(mtl, largest = T)

DA_mtl %>% select(NOM, GeoUID) %>% st_drop_geometry()  %>% filter(!is.na(NOM))
DA_MTL_Key <- unique(DA_mtl[, c('NOM', 'GeoUID', "CT_UID", "Population")]) %>% st_drop_geometry() %>% filter(!is.na(NOM)) 
#DA_MTL_Key <- unique(DA_mtl[, c('NOM', 'GeoUID')]) %>% st_drop_geometry() %>% filter(!is.na(NOM)) 
DA_MTL_Nom_pop_Key <- unique(DA_MTL_Key[, c('NOM', "Population")]) %>% st_drop_geometry() %>% filter(!is.na(NOM)) %>% group_by(NOM) %>%   
  summarise(Population = sum(Population), .groups = 'drop')
length(unique(DA_MTL_Key$GeoUID))

library(dplyr)

routing$area <- as.character(routing$area)
routing$home_area <- as.character(routing$home_area)

joined_Data_b <- routing %>%
  left_join(DA_MTL_Key, by = c("area" = "GeoUID")) %>%
  rename("CT_UID_area" = "CT_UID") %>%
  rename("NOM_area" = "NOM") 

# Join on 'home_area'
final_Data_b <- joined_Data_b %>%
  left_join(DA_MTL_Key, by = c("home_area" = "GeoUID")) %>%
  rename("CT_UID_home_area" = "CT_UID") %>%
  rename("NOM_home_area" = "NOM") 

final_Data_b <- final_Data_b %>%
  select(row.names, source, area, home_area, stops, province, y, m,
         CT_UID_area, CT_UID_home_area, NOM_area, NOM_home_area)

DA_clean_data <- final_Data_b %>% filter(!is.na(NOM_area)) %>% filter(!is.na(NOM_home_area))
routing_2021_clean_data <- DA_clean_data %>%
  group_by(NOM_area, NOM_home_area) %>%   
  summarise(stops = sum(stops), .groups = 'drop') #weight/CT_UID_area
max(routing_2021_clean_data$stops) #edges

routing_2021_clean_data <- routing_2021_clean_data %>%
  left_join(DA_MTL_Nom_pop_Key, by = c("NOM_area" = "NOM")) %>%
  rename("Population_area" = "Population") 
routing_2021_clean_data <- routing_2021_clean_data %>%
  select(NOM_area, NOM_home_area, stops, Population_area)
# Weighted by population_area
routing_2021_clean_data$stops_W <- routing_2021_clean_data$stops/sum(routing_2021_clean_data$Population_area)*routing_2021_clean_data$Population_area
summary(routing_2021_clean_data$stops_W)

routing_2021_clean_data_loop <- routing_2021_clean_data %>% filter(NOM_area == NOM_home_area) 
new_row <- data.frame( NOM_area = "L'ﾃ四e-Dorval",
                       NOM_home_area = "L'ﾃ四e-Dorval",
                       stops = 0,
                       Population_area=30,
                       stops_W=0) # L'ﾃ四e-Dorval has 0
routing_2021_clean_data_loop <- rbind(routing_2021_clean_data_loop, new_row)

```

```{r}
library(igraph)
library(visNetwork)

edges <- unique(routing_2021_clean_data[, c("NOM_area", "NOM_home_area", "stops", "stops_W")]) 
nodes <- routing_2021_clean_data_loop %>% select(NOM_area, stops, stops_W)
summary(routing_2021_clean_data$stops_W)

network <- graph_from_data_frame(edges, nodes, directed = TRUE)
#V(network)$stops
#E(network)

net <- simplify(network, remove.multiple = F, remove.loops = T) 

#Reduce Edge Density
# Filter edges based on a weight threshold
edge_threshold <- 0.86583  # Set a threshold for edge weight(First 25%)
filtered_edges <- E(net)[stops_W > edge_threshold] # only plot stops > 5

# Create a subgraph with only the filtered edges
net_filtered <- subgraph.edges(net, filtered_edges, delete.vertices = FALSE)

# Plot the filtered graph

set.seed(123)
# Highlight nodes with high degrees or other centrality measures.
# Calculate degree centrality
degree_centrality <- degree(net_filtered)
V(net_filtered)$size <- degree_centrality / max(degree_centrality) * 10 + 5  # Scale node size
V(net_filtered)$color <- "lightblue"

# Using visNetwork for interactive plotting

# Convert igraph to visNetwork
vis_data <- toVisNetworkData(net_filtered)
nodes <- vis_data$nodes
edges <- vis_data$edges
# Create interactive network

# Add stops to the label
#nodes$label <- paste(nodes$label, nodes$stops, sep = ": Stops=")
nodes$label <- paste(nodes$stops)
length(nodes$stops)
visNetwork(nodes, edges) %>%
  visEdges(scaling = list(min = 2, max = 10)) %>%
  visNodes(scaling = list(min = 10, max = 30)) %>%
  visOptions(highlightNearest = TRUE, nodesIdSelection = TRUE)

map_nodes <- function(edges,nodes) {
  mtl_sf <- st_as_sf(mtl)
  
  # Extract centroids for each state to use as node coordinates
  mtl_geo_key <- unique(mtl[, c('NOM', "geometry")])
  
  nodes <- nodes  %>%
    left_join(mtl_geo_key, by = c("id" = "NOM")) 
  nodes_sf <- st_as_sf(nodes)
  nodes$geometry <- st_centroid(nodes$geometry)
  
  edges <- edges %>%
    left_join(mtl_geo_key, by = c("from" = "NOM")) %>%
    rename(from_geo = geometry) %>%
    left_join(mtl_geo_key, by = c("to" = "NOM")) %>%
    rename(to_geo = geometry) 
  
  edges_sf <- st_as_sf(edges)
  
  edges_sf$geometry <- mapply(function(from, to) {
    from_coords <- st_coordinates(st_centroid(from))
    to_coords <- st_coordinates(st_centroid(to))
    st_linestring(rbind(from_coords, to_coords))
  }, edges$from_geo, edges$to_geo, SIMPLIFY = FALSE)
  
  #edges_sf <- edges  %>% st_as_sf(coords = c(from_cor, to_cor), crs = 2959)
  edges_sf <- st_as_sfc(edges_sf$geometry, crs = 2959)
  edges_sf <- st_as_sf(edges_sf, crs = 2959)
  
  ggplot() +
    geom_sf(data = mtl) +
    geom_sf(data = edges_sf, color = "blue") +
    geom_sf(data = nodes$geometry) +
    geom_text(data = nodes, aes(x = st_coordinates(geometry)[,1], 
                                y = st_coordinates(geometry)[,2], 
                                label = label), size = 3, vjust = -1) +
    ggtitle("2021 25% Network Flow Plot", subtitle = "from July to November") +
    #geom_text(data = nodes, aes(label = label), size = size, hjust = 1.5) +
    scale_size_continuous(range = c(0.5, 3)) +
    scale_color_identity() +
    theme_map() +
    theme(legend.position = "none")
}

map_nodes(edges,nodes)
```

```{r}
adjacency_matrix <- as.matrix(as_adjacency_matrix(network, attr="stops"))
#adjacency_matrix <- as.matrix(as_adjacency_matrix(net_filtered, attr="stops"))
adjacency_matrix
#diag(adjacency_matrix) <- DA_clean_data_m1_5_loop$stops
```

```{r}
# Create a symmetric matrix by adding the matrix to its transpose
symmetric_matrix <- adjacency_matrix + t(adjacency_matrix)

# If you want to ensure the diagonal remains the same as in the original matrix (optional)
diag(symmetric_matrix) <- diag(adjacency_matrix)

# Display the symmetric matrix
symmetric_matrix

```


## use traditional contiguity based neighbourhood matrix as the benchmark spatial model (rather based on graph edge mobility neighbour)
### generated weight mx
```{r}
library(spdep)
nb <- spdep::poly2nb(mtl, queen = TRUE)
head(nb) # For nb[[i]], it will list the indices of the polygons that are adjacent to the i-th polygon.
plot(st_geometry(mtl), border = "lightgray")
plot.nb(nb, st_geometry(mtl), add = TRUE)
nb
```

```{r}
# Convert neighbors list to adjacency matrix
adj_matrix <- nb2mat(nb, style = "B")

# Display the adjacency matrix
adj_matrix #  The indices refer to the row numbers of the spatial polygons in the mtl object.
```

```{r}
summary(adj_matrix )
```

